---
title: "worldflora_failure"
author: "carrie lu"
date: "2024-03-07"
output: html_document
---

```{r}

#install.packages("Rcmdr", dependencies = TRUE)
#library(Rcmdr)

# install.packages("WorldFlora", dependencies = TRUE)
#library(WorldFlora)

#library(RcmdrPlugin.WorldFlora)

#this didnt work I couldn't use it 

```
```
```{r}
# Read the original CSV file
conserve <- read.csv("C:/Users/14159/OneDrive/Desktop/project/conservatory_data.csv", header = TRUE)

# Replace empty cells with NA
conserve[conserve == ""] <- NA

# Write the modified data frame to a new CSV file
#write.csv(conserve, "C:/Users/14159/OneDrive/Desktop/project/conservatory_modified.csv", row.names = FALSE)

```

```{r}
# Read the original CSV file
conserve2 <- read.csv("C:/Users/14159/OneDrive/Desktop/project/conservatory_modified.csv", header = TRUE)

# Combine "number of" and "form" into a single column
conserve2$combined_column <- paste(conserve2$number, conserve2$form, sep = " ")

# Remove the original "number of" and "form" columns
conserve2 <- conserve2[, -c(which(names(conserve2) %in% c("number", "form")))]

# Write the modified data frame to a new CSV file
#write.csv(conserve, "C:/Users/14159/OneDrive/Desktop/project/conservatory_modified.csv", row.names = FALSE)

```


```{r}
#make a new one from modified

library(dplyr)

# Read the original CSV file and remove rows with NA values in the "form" column
conserve3 <- read.csv("C:/Users/14159/OneDrive/Desktop/project/conservatory_modified.csv", header = TRUE) %>%
  filter(!is.na(form))

# Split the "form" column into four separate columns
conserve3 <- conserve3 %>%
  mutate(
    cutting = if_else(grepl("cutting", form, ignore.case = TRUE), "cutting", NA_character_),
    seedling = if_else(grepl("seedling", form, ignore.case = TRUE), "seedling", NA_character_),
    seed = if_else(grepl("seed", form, ignore.case = TRUE), "seed", NA_character_),
    plant = if_else(grepl("plant", form, ignore.case = TRUE), "plant", NA_character_),
    bulb = if_else(grepl("bulb", form, ignore.case = TRUE), "bulb", NA_character_)
  ) %>%
  select(-form)

# Write the modified data frame to a new CSV file
#write.csv(conserve3, "C:/Users/14159/OneDrive/Desktop/project/conservatory_newest.csv", row.names = FALSE)

#also number is the number of ____
```

```{r}
# Load necessary libraries
library(ggplot2)

# Read the CSV file
conserve4 <- read.csv("conservatory_newest.csv", header = TRUE)

# Count the number of occurrences of each category
category_counts <- colSums(!is.na(conserve4[, c("cutting", "seedling", "seed", "plant", "bulb")]))

# Convert the counts to a data frame
category_counts_df <- data.frame(Category = names(category_counts), Count = category_counts)

ggplot(category_counts_df, aes(x = Category, y = Count)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(title = "Count of Different Categories",
       x = "Category",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```



